Approximation as Differentiation

### 2025-05-06 appendix/notes/auto-diff.tex
(strictly) indexed categories.

\todo{The reason we can't combine $\Diff$ and $\Diff^*$ into a single category, with morphisms $f: \RR^m \to \RR^n \times (\RR^m \linearto \RR^n) \times (\RR^n \linearto \RR^m)$ is..?}

>>>>

\todo{Can't combine $\Diff$ and $\Diff^*$ into a single subcategory of $\Fam(\FinVect)$, with morphisms $f: \RR^m \to \RR^n \times (\RR^m \linearto \RR^n) \times (\RR^n \linearto \RR^m)$, because $\Fam(\FinVect)$ is not Cartesian closed?}
